\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\huge Majd Yousof}
\end{center}

\begin{center}

\href{https://majdyousof.github.io}{\underline{majdyousof.github.io}} $|$
\href{mailto:majdyousof@gmail.com}{majdyousof@gmail.com} $|$
\href{https://www.linkedin.com/in/majdyousof/}{www.linkedin.com/in/majdyousof} $|$
\small 07841611162 $|$
\small London, UK 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MEng Civil Engineering $|$ Imperial College London}{OCT 2021 -- JUN 2025}
      {Predicted Grade: $\mathbf{1^{st}}$, Third year grade: $\mathbf{1^{st}}$}{}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis Title:} Conditional benchmarking of public transport performance using Machine Learning algorithms.}
        \resumeItem{\textbf{Relevant Modules:} Machine Learning, Operations Research and Systems Analysis, Transport Demand and Economics, Computational Methods, Mathematics, Statistics.}
        \resumeItem{President's Black Heritage Scholarship and Peter Fraenkel Prize recipient.}
        \resumeItemListEnd

    \resumeSubheading
        {A-Levels $|$ Dunraven School}{SEP 2019 -- JUN 2021}
        {Mathematics (A*), Further Mathematics (A*), Physics (A*)}{}
  \resumeSubHeadingListEnd


%-----------Professional Experience-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern $|$ \textit{Maven Securities}}{JUN 2024 -- AUG 2024}
      {}{}
      \resumeItemListStart
        \vspace{-4mm}
        \resumeItem{Designed and implemented a new internal technology support portal to replace a third-party service, saving the company \textbf{£20,000+} per annum finishing the project \textbf{3 weeks} ahead of schedule.}
        \resumeItem{Successfully created and pitched an MVP for a new internal permissions management system to provide self service for employees to reduce the amount of related tickets within \textbf{2 weeks}.}
        \resumeItem{Liased with internal stakeholders to gather requirements and feedback, leading to a \textbf{90\%} satisfaction rate.}
        \resumeItem{Attended C\#, C++, React and Options Market Making training sessions to improve technical knowledge.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Undergraduate Researcher $|$ \textit{Imperial College London}}{JUN 2023 -- SEPT 2023}
      {}{}
      \resumeItemListStart
        \vspace{-4mm}
        \resumeItem{Recieved the President's Black Heritage Scholarship award to conduct a research project investigating the Granger causal relationship between mobility and COVID-19 using novel methods.}
        \resumeItem{Authored a paper that was accepted into the International Conference of Hong Kong Society for Transport Studies for oral presentation (\href{https://www.hksts.org/conf23l.pdf}{\underline{https://www.hksts.org/conf23l.pdf}}) although unable to personally attend due to unforeseen circumstances.}
        \resumeItem{Analyzed and visualized \textbf{10GB+} of data using Python and R to run statistical tests and identify trends.}
      \resumeItemListEnd

      \resumeSubheading
      {Technology Spring Intern $|$ \textit{Maven Securities}}{APR 2023 -- APR 2023}
      {}{}
      \resumeItemListStart
        \vspace{-4mm}
        \resumeItem{Selected as \textbf{one of 15} to attend the technology insight programme.}
        \resumeItem{Participated in a \textbf{3-hour hackathon} analysing PCAP files in Python, resulting in a return offer.}
      \resumeItemListEnd

      \resumeSubheading
      {Technology Spring Intern $|$ \textit{JP Morgan \& Chase}}{APR 2023 -- APR 2023}
      {}{}
      \resumeItemListStart
        \vspace{-4mm}
        \resumeItem{\textbf{Top 2.5\%} of applicants in the UK invited to attend the technology insight programme.}
        \resumeItem{Participated in a \textbf{12-hour hackathon}, focusing on the backend of a web app using Flask and SQLite3.}
    
      \resumeItemListEnd

      \resumeSubheading
      {Spring Intern $|$ \textit{Deloitte}}{APR 2023 -- APR 2023}
      {}{}
      \resumeItemListStart
        \vspace{-4mm}
        \resumeItem{\textbf{One of 34} students in the UK invited to the Black Business Professionals insight programme.}
        \resumeItem{Pitched a consulting presentation to senior professionals following a rigorous SWOT and PESTEL analysis of a start-up.}
    
      \resumeItemListEnd

  \resumeSubHeadingListEnd


% -----------Leadership and extracurricular-----------
\section{Leadership and Extracurricular}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Vice President $|$ STEMMuslims}{OCT 2023 -- JUN 2024}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Led a team of \textbf{10} committee members to organize and host \textbf{10+} events with major consulting (\textbf{MBB}), tech (\textbf{Amazon, IBM etc.}) and scientific companies as well as academics from renowned institutions (\textbf{Oxford, Caltech etc.}) and journals (\textbf{Nature Cell Biology}).}
        \resumeItem{Organised and hosted a \textbf{300+} attendee flagship careers fair with \textbf{8 keynote talks} and \textbf{15+ stalls}, recieving incredible feedback from both attendees and stall vendors.}
      \resumeItemListEnd

      \resumeSubheading
      {Sponsorship Officer (Founding Member) $|$ STEMMuslims }{OCT 2022 -- JUN 2023}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Planned and executed a hybrid speaker event with \textbf{40+} attendees, resulting in the speaker's offer to personally submit \textbf{10
        CVs} to Jacobs KSA HR afterwards due to its exceptional outcome.}
        \resumeItem{Coordinated a successful joint event with a fintech firm achieving \textbf{100+} participants on campus, and subsequently earned
        an invitation to visit the company's UK headquarters to meet with top executives.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------Skill and Interests-----------
\section{Achievements, Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Technical Skills}{: Python, MATLAB, R, C\# (.NET, ASP.NET), C++, Typescript, React, Kubernetes, \LaTeX.} \\
     \vspace{1mm}
      \textbf{Achievements}{: Peter Fraenkel Prize for \textbf{Best Third Year Group Project} (2024), Design Week \textbf{Best Crane (2022)}.} \\
     \textbf{Interests}{: Fashion, PC building, Wood Carving, Gym.} \\
     \vspace{1mm}

    }}
 \end{itemize}

\end{document}